Self Regulation Ontology Retest Data Report

### 2018-01-15 code/SRO_Report.Rmd
updated pipeline notes and paths

```{r}
hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/hddm_refits_exhaustive.csv')

>>>>

```{r}
hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/hddm_refits_exhaustive.csv')
